RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-09-16 formalframework.tex
small changes + reference inference engine

We use formal logic (propositional logic) to specify our framework, and in order to develop our tool we have implemented an algorithm to compute argumentation extensions based on this formalization. However, we do not use a dedicated theorem prover or a logical inference engine. The reason is purely practical, it is our aim to develop a tool that practitioners can use in their browser, and it does not seem necessary nor useful to use an external theorem prover for this. Instead, in this section we propose algorithms based on our logical specification, which form the basis of our prototype implementation.

>>>>

We use formal logic (propositional logic) to specify our framework, and we have implemented an algorithm to compute argumentation extensions based on this formalization. However, we do not use a dedicated logical inference engine for argumentation (see e.g. \cite{hecham2018first}). The reason is that, in the current paper, our is to aim to develop a tool that users can use in their browser, and that hence the focus is not on developing a complete logical inference engine for, for example, automatically deriving goals from tasks. Instead, we propose algorithms based on our logical specification, which form the basis of our prototype implementation.
